% Created 2017-10-02 Mon 14:31
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{enumitem}
\date{}
\title{Yeongho Kim}
\hypersetup{
 pdfauthor={Yeongho Kim},
 pdftitle={Yeongho Kim},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.3.1 (Org mode 9.1.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{itemize}[label=\null,itemsep=-1ex]
\item yeonghoey@gmail.com
\item yeonghoey.com
\item github.com/yeonghoey
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

\begin{quote}
Aliquam erat volutpat.  Nunc eleifend leo vitae magna.  In id erat non orci commodo lobortis.  Proin neque massa, cursus ut, gravida ut, lobortis eget, lacus.  Sed diam.  Praesent fermentum tempor tellus.  Nullam tempus.  Mauris ac felis vel velit tristique imperdiet.  Donec at pede.  Etiam vel neque nec dui dignissim bibendum.  Vivamus id enim.  Phasellus neque orci, porta a, aliquet quis, semper a, massa.  Phasellus purus.  Pellentesque tristique imperdiet tortor.  Nam euismod tellus id erat.
\end{quote}


\newpage

\section*{Experience}
\label{sec:org5dff189}
\subsection*{\underline{\href{https://github.com/what-studio}{What! Studio}}}
\label{sec:orge076103}
\subsubsection*{Data and DevOps Engineer | June 2016 – Present}
\label{sec:orga945d0d}
In charge of infrastructures for \uline{\href{https://durango.nexon.com/en}{Durango: Wild Lands}}, a seamless open world \emph{MMORPG}.

\begin{itemize}
\item Built data pipelines for time series data which are generated by distributed game servers. Based on
\emph{Fluentd}, \emph{Amazon Kinesis Streams}, \emph{AWS Lambda}, \emph{Elasticsearch}, \emph{Spark} and \emph{Zeppelin}.
\item Managed infrastructures (>200 instances) across on \emph{AWS} (>15 services) via \emph{Terraform}.
\item Maintained \emph{Couchbase}, the game's main NoSQL Database, to set up, scale up and out,  monitor / tune performance, etc.
\item Evangelized readable, maintainable code styles in \emph{Python}
\end{itemize}

\subsection*{\underline{\href{http://frograms.com}{FROGRAMS}}}
\label{sec:orgcc8595d}
\subsubsection*{Software Engineer  | November 2015 – May 2016}
\label{sec:orgd8a6716}
Improved code quality for the recommendation engine of \uline{\href{https://watcha.net/}{WATCHA}} and \uline{\href{https://play.watcha.net}{WATCHA PLAY}},
a Netflix-like movie recommendation and streaming service in Korea.

\begin{itemize}
\item Drafted \emph{Scala} coding standard and made guidelines for the team.
\item Introduced \emph{Scala} code quality tools like \emph{scalafmt}, \emph{scalariform}
\item Introduced testing frameworks like \emph{Specs2}, \emph{ScalaCheck}
\item Did lots of refactoring on \emph{Scala} codebase which is based on \emph{Finagle}, high-concurrency RPC framework by \emph{Twitter}.
\item Built CI/CD pipeline for the recommendation engine with \emph{Jenkins}, \emph{supervisord}
\end{itemize}

\subsection*{\href{http://company.nexon.com/Eng/}{NEXON Korea}}
\label{sec:org3d4d3e5}
\subsubsection*{Game Developer  | December 2013 – November 2015}
\label{sec:org5f7edcf}
Broad range of game development for \href{http://bf.nexon.com}{Bubble Fighter}, A casual TPS Game written in \emph{C++}.

\begin{itemize}
\item Designed and implemented Intelligent Matchmaking System based on \emph{TrueSkill}.
Gave a presentation about it on \uline{\href{http://ndcreplay.nexon.com/NDC2015/sessions/NDC2015\_0048.html}{NEXON Developers Conference 2015}} (Korean)
\item Wrote anti-hacking codes including memory encryption, hash validation for game data.
\item Optimized the games's network performance to cope with severe network conditions when localizing for Indonesia.
\end{itemize}
\end{document}
